<<<<<<< HEAD
# Reproducible research assignment 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev = c('png'))
knitr::opts_chunk$set(fig.path="figures/")
```

## 1. Loading and preprocessing the data

This code is used to load the data and process thedata
```{r loaddata}
data <- read.csv("activity.csv",na.strings = "NA")
summary(data)
```

## 2. What is mean total number of steps taken per day

```{r plot}
stepday <- tapply(data$steps,data$date,sum,na.rm=TRUE)
hist(stepday,breaks=20,xlab = "number of steps")
```

This is to calculate the median and mean of total number of steps

```{r median}
median(stepday)
```
```{r mean}
mean(stepday)
```

## 3. What is the average daily activity pattern?
### make the plot
```{r interval}
data$interval <- as.factor(data$interval)
interstep <- tapply(data$steps,data$interval,mean,na.rm=TRUE)
plot(as.numeric(unique(data$interval)),interstep,type="l",xlab="interval",ylab="average number of steps")
```

### which contains the maximum
```{r findmax}
interstep[which.max(interstep)]
```

## 4. Imputing missing values
### total nubmer of missing values
```{r missing}
sum(is.na(data$steps))
```

### fill the missing value based on mean of the 5 min interval

```{r filldata}
newdata <- data
naindex <- which(is.na(data$steps))
xy <- data$interval[naindex]
xy <- as.character(data$interval[naindex])
substi <- as.numeric(vector())
for (i in xy){substi <- c(substi,interstep[i])}
newdata$steps[naindex] <- substi
summary(newdata)
```

### plot histogram

```{r plotfilled}
newstep <- tapply(newdata$steps,newdata$date,sum)
hist(newstep,breaks = 20,xlab = "number of steps")
```

mean and median total number of steps taken per day
```{r mean2}
mean(newstep)
```

```{r median2}
median(newstep)
```

Both values shifted compared with the previous results

## 5. Are there differences in activity patterns between weekdays and weekends

### Create new factor variable

```{r factor weekday}
weekday <- c("Monday","Tuesday","Wednesday","Thursday","Friday")
weekend <- c("Saturday","Sunday")
week <- as.character(weekdays(as.Date(data$date)))
week[week %in% weekday] <- "weekday"
week[week %in% weekend] <- "weekend"
data$newcolumn <- week
head(data)
```

```{r factor}
levels(as.factor(data$newcolumn))
```

### Make new plot for weekday and weekends

```{r}
library(reshape2)
groupinter <- tapply(data$steps,list(data$interval,data$newcolumn),mean,na.rm=TRUE)
groupinter <- data.frame(groupinter)
groupinter <- cbind(groupinter,unique(data$interval))
names(groupinter)[3] <- "interval"
melted <- melt(groupinter,id.vars = "interval" ,variable.name = "time", value.name = "steps")
head(melted)
```

```{r plotweekend}
library(lattice)
melted$interval <- as.numeric(melted$interval)
xyplot(steps~interval|time,melted,type="l",layout=c(1,2),scales =list(x=list(tick.number=5, tck=0.1)))
```



